### 2021-08-07 paper/paper.tex
cite Liu, Lu, Shu (2021) for the jet problem

Figure~\ref{fig:jet} demonstrates demonstrates entropy-dissipative shock-capturing
methods with positivity-preserving limiters and adaptive mesh refinement applied
to an astrophysical supersonic jet with Mach number 2000.
\begin{figure}[!h]
  \begin{subfigure}{0.53\linewidth}
    \includegraphics[width=\textwidth]{../figures/jet_density}
    \caption{Density at time $t = 10^{-3}$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.47\linewidth}
    \includegraphics[width=\textwidth]{../figures/jet_mesh}
    \caption{Mesh at time $t = 10^{-3}$.}
  \end{subfigure}%
  \caption{Numerical solutions of a supersonic jet with Mach number 2000 using
           entropy-dissipative shock-capturing methods with positivity-preserving
           limiters and adaptive mesh refinement for the compressible Euler equations.}
  \label{fig:jet}
\end{figure}

>>>>

Figure~\ref{fig:jet} demonstrates demonstrates entropy-dissipative shock-capturing
methods with positivity-preserving limiters and adaptive mesh refinement applied
to an astrophysical supersonic jet with Mach number 2000 \cite{liu2021oscillation}.
\begin{figure}[!h]
  \begin{subfigure}{0.53\linewidth}
    \includegraphics[width=\textwidth]{../figures/jet_density}
    \caption{Density at time $t = 10^{-3}$.}
  \end{subfigure}%
  \hspace*{\fill}
  \begin{subfigure}{0.47\linewidth}
    \includegraphics[width=\textwidth]{../figures/jet_mesh}
    \caption{Mesh at time $t = 10^{-3}$.}
  \end{subfigure}%
  \caption{Numerical solutions of a supersonic jet with Mach number 2000 using
           entropy-dissipative shock-capturing methods with positivity-preserving
           limiters and adaptive mesh refinement for the compressible Euler equations.}
  \label{fig:jet}
\end{figure}
